---
title: "Untitled"
author: "Malte Söhren"
date: "10/16/2020"
output: html_document
---
# Loading Packages 

```{r}
library(tidyverse)
library(DataExplorer)
library(caret)
library(caretEnsemble)
library(pROC)
library(gbm)
library(data.table)
library(superml)
```

```{r}
setwd("/Users/2egaa/Desktop/BotorNot/")
data_base <- read.csv("botornot-1.csv")
```

# Data Cleaning 

Identify relevant variables on theoretical note 

```{r}
data <- data_base %>%  select(c(bot, overallTime, consentTime, readProfileTime, readEssayTime, speeder, superspeeder, quirk, age, birthday, birthmonth, gender, totlanguage, god, grownup_us, samestate, sametown, incomeclass, retake, session, disconnected, treatment, feedback, grownup_us, parentsdivorced, children, pets.0, military, gayfriends, incomebracket, income,  session))
```

Recode NA's in bot column as zeros 

```{r}
data$bot[is.na(data$bot)] <- 0
data$bot[data$bot == 2] <- 1
data$bot[data$bot == 3] <- 1

data$bot <- as.factor(data$bot)

data$bot <- factor(data$bot, levels=c(0,1), labels=c("No", "Yes"))
data$speeder <- as.factor(data$speeder)
data$superspeeder <- as.factor(data$superspeeder)
data$retake <- as.factor(data$retake)
```

Remove NA Rows

```{r}
data <- data %>% na.omit()
```

Count words in quirk variable

```{r}
data <- data %>% mutate(quirk_count = sapply(gregexpr("\\S+", data$quirk), length), feedback_count = sapply(gregexpr("\\S+", data$feedback), length))

```

# Short summary

```{r}
data %>% group_by(bot) %>% 
         summarize(overalltime = median(overallTime),
                   consenttime = median(consentTime), 
                   readProfileTime = median(readProfileTime), 
                   readEssayTime = median(readEssayTime), 
                   speeder = mean(as.numeric(speeder)), 
                   superspeeder = mean(superspeeder), 
                   quirk_count = mean(quirk_count),
                   age = median(age))
```

# Some Plotting 

```{r}
 ggplot(data, aes(x = bot, y = consentTime)) + geom_boxplot(outlier.shape = NA) + scale_y_continuous(limits = quantile(data$consentTime, c(0.1, 0.9)))

plotdata <- data %>% select(c(bot, consentTime, readProfileTime, readEssayTime, quirk_count, feedback_count, age))

df.m <- melt(plotdata, id.var = "bot", factorsAsStrings=F)

ggplot(data = df.m, aes(x=variable, y=value)) + geom_boxplot(aes(fill=bot)) + scale_y_continuous(limits = quantile(plotdata$consentTime, c(0.1, 0.9)))
```

# Some wrangeling and Bag of Words

```{r}
cv <- CountVectorizer$new(max_features = 300, remove_stopwords = FALSE)

bow <- cv$fit_transform(data$feedback)

bow <- as.data.frame(bow)

modeldata <- bind_cols(data, bow)
modeldata <- modeldata %>% select(-c(quirk, feedback...23))

colnames(modeldata) <- make.names(colnames(modeldata))
```

# Setting up modeling 

Split data into train & test set. Here, a 70/30 split is used to provide the test set with some more cases of the minority class (80/20-split would have resulted in only 14 cases which the model can be tested on)

```{r}
set.seed(92385)

cdp <- createDataPartition(modeldata$bot, 
                               p = .7, 
                               list = FALSE, 
                               times = 1)

model_train <- modeldata[cdp,]
model_test <- modeldata[-cdp,]
```

Defining the control object. Here, I am chossing 5-fold cross validation as well as SMOTE to create synthetic cases for the minority class.

```{r}
ctrl  <- trainControl(method = "cv", 
                      number = 5,
                      summaryFunction = twoClassSummary,
                      verboseIter = TRUE,
                      classProbs = TRUE,
                      sampling = "smote",
                      savePredictions = "final")
```

# Train models 

## KNN 

```{r}
set.seed(28938)

knn <- train(bot ~ .,
             data = model_train,
             method = "knn",
             trControl = ctrl,
             preProcess = c("center","scale"),
             metric = "ROC")
```

```{r}
p_knn <- predict(knn, model_test, type = "raw")
confusionMatrix(p_knn, model_test$bot, mode = "everything", positive = "Yes")

prob_knn <- predict(knn, model_test, type = "prob")
```

## Adaboost

Train model

```{r}
set.seed(54637)

ada <- train(bot ~ .,
             data = model_train,
             method = "ada",
             trControl = ctrl,
             metric = "ROC")
```

Predict 

```{r}
p_ada <- predict(ada, census_test, type = "raw")
confusionMatrix(p_ada, census_test$bot, mode = "everything", positive = "Yes")
```

```{r}
prob_ada <- predict(ada, newdata = census_test, type = "prob")
prob_ada
```

# XGBoost 

```{r}
grid_xg <- expand.grid(max_depth = c(2, 3, 5),
                    nrounds = c(100, 250),
                    eta = c(0.05, 0.1, 0.3),
                    min_child_weight = c(1, 2, 3),
                    subsample = 0.7,
                    gamma = c(0, 0.5),
                    colsample_bytree = c(0.4, 1.0),
                    subsample = c(0, 0.5))
```

```{r}
set.seed(79647)
xgb <- train(bot ~ .,
             data = model_train,
             method = "xgbTree",
             trControl = ctrl,
             tune = grid_xg,
             metric = "ROC")

#    nrounds max_depth eta gamma colsample_bytree min_child_weight
#         50         3 0.4     0              0.8                1
    subsample
#           1
```

```{r}
p_xgb <- predict(xgb, newdata = model_test, type = "raw")
confusionMatrix(p_xgb, model_test$bot, mode = "everything", positive = "Yes")

prob_xgb <- predict(xgb, newdata = model_test, type = "prob")
round(prob_xgb, 2)

```

## C5.0

```{r}
set.seed(87543)

c5 <- train(bot ~ .,
            data = model_train,
            method = "C5.0",
            trControl = ctrl)
```

```{r}
p_c5 <- predict(c5, model_test, type = "raw")
confusionMatrix(p_c5, model_test$bot, mode = "everything", positive = "Yes")

prob_c5 <- predict(c5, model_test, type = "prob")
bind_cols(round(prob_c5, 2), model_test$bot)

```

## Extra-Trees 

```{r}
grid_et <- expand.grid(mtry = c(2,4,6, 8, 10, 12),
                    splitrule = c("extratrees"),
                    min.node.size = c(5,10,20))
grid_et
```

```{r}
set.seed(87543)
et <- train(bot ~ .,
            data = model_train,
            method = "ranger",
            trControl = ctrl,
            tuneGrid = grid_et)
```

```{r}
p_et <- predict(et, model_test, type = "raw")
confusionMatrix(p_et, model_test$bot, mode = "everything", positive = "Yes")

prob_et <- predict(et, model_test, type = "prob")

```

Creating ROC Objects. 

```{r}
xgb_roc <- roc(model_test$bot, prob_xgb$Yes)
ada_roc <- roc(model_test$bot, prob_ada$Yes) 
knn_roc <- roc(model_test$bot, prob_knn$Yes)
c5_roc <- roc(model_test$bot, prob_c5$Yes)
et_roc <- roc(model_test$bot, prob_et$Yes)
ens_roc <- roc(model_test$bot, prob_ens$Yes)
```

Plotting ROC Objects. 

```{r}
ggroc(list(XGB = xgb_roc, 
           C5.0 = c5_roc,
           ExtraTrees = et_roc,
           KNN = knn_roc)) +
  geom_segment(aes(x = 1, xend = 0, y = 0, yend = 1), 
               color="darkgrey", linetype="dashed") +
  theme(legend.title = element_blank())
```


Variablle Importance 

```{r}
gbmImp <- varImp(c5, scale = FALSE)
plot(gbmImp)
gbmImp
```





# Things I am trying out right now (Stacking models)

```{r}
model_list <- caretList(bot ~ .,
                        data = model_train,
                        trControl = ctrl,
                        metric = "ROC",
                        methodList = c("C5.0", "ranger", "gbm"))
```

```{r}
glm_ensemble <- caretStack(model_list,
                           method = "xgbTree",
                           trControl = trainControl(
                              method = "cv",
                              number = 5,
                              savePredictions = "final",
                              verboseIter = TRUE,
                              classProbs = TRUE,
                              summaryFunction = twoClassSummary),
                           tune = expand.grid(max_depth = c(2, 3, 5),
                              nrounds = c(100, 250),
                              eta = c(0.05, 0.1, 0.3),
                              min_child_weight = c(1, 2, 3),
                              subsample = 0.7,
                              gamma = c(0, 0.5),
                              colsample_bytree = c(0.4, 1.0),
                              subsample = c(0, 0.5)))
```

```{r}
glm_ensemble
coef(glm_ensemble$ens_model$finalModel)
```

```{r}
p_ens <- predict(glm_ensemble, newdata = model_test, type = "raw")
confusionMatrix(p_ens, model_test$bot, mode = "everything", positive = "Yes")

prob_ens <- predict(glm_ensemble, model_test, type = "prob")

prob_et <- predict(et, model_test, type = "prob")

```



Start the tuning process.



